### 2013-12-13 Docs/introduction/introduction.tex
some text about the new energy formulation

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2011, ApJ,
  740, 8 (henceforth paper V)
\item {\em High-Resolution Simulations of Convection Preceding Ignition in
  Type Ia Supernovae Using Adaptive Mesh Refinement,}
  A. Nonaka, M. Zingale, A. J. Aspden, A. S. Almgren, J. B. Bell, \& S. E. Woosley 2012, 
  ApJ, 745, 73
\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasehkar White Dwarfs. I. Methodology,} M.~Zingale,
  A.~Nonaka, A.~S.~Almgren, J.~B.~Bell, C.~M.~Malone, \&
  R.~J.~Orvedahl 2013, ApJ, 764, 97
\item {\em Low-Mach Number Modeling of Core Convection in Massive Stars,}
  C.~Gilet, A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, S.~E.~Woosley, \& M. Zingale
  2013, ApJ, submitted.
\end{itemize}

@@

>>>>

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2011, ApJ,
  740, 8 (henceforth paper V)
\item {\em High-Resolution Simulations of Convection Preceding Ignition in
  Type Ia Supernovae Using Adaptive Mesh Refinement,}
  A. Nonaka, M. Zingale, A. J. Aspden, A. S. Almgren, J. B. Bell, \& S. E. Woosley 2012, 
  ApJ, 745, 73
\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasehkar White Dwarfs. I. Methodology,} M.~Zingale,
  A.~Nonaka, A.~S.~Almgren, J.~B.~Bell, C.~M.~Malone, \&
  R.~J.~Orvedahl 2013, ApJ, 764, 97
\item {\em Low-Mach Number Modeling of Core Convection in Massive Stars,}
  C.~Gilet, A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, S.~E.~Woosley, \& M. Zingale
  2013, ApJ, 773, 137
\end{itemize}

@@

\subsection{Alternate Energy Formulation}

Several authors~\cite{KP:2012,VLBWZ:2013} showed that with a slightly
different momentum equation, the low Mach number system can conserve
an energy (that is, a quantity that looks like the compressible
energy, but formed using the low Mach number quantities).  This change
manifests itself as either a change to the buoyancy term or by
changing $\nabla \pi$ to $\beta_0 \nabla (\pi/\beta_0)$.  Furthermore,
\cite{VLBWZ:2013} showed that the new formulation better captures the
vertical propagation of gravity waves.  We explored this in more
detail and from an asymptotic approach in \cite{MaestroEnergy}.  As of
Dec.\ 2013, this new formulation is the default in \maestro.
